Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-09-30 latex/robdml.tex
tex
make lyx table only

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}

@@

% contributions
In brief, our contribusions include:
%
\begin{enumerate}
	%
	\item Hardness manipulation and the finding. better robustness.
		%
	\item Combine and even better.
		%
	\item Accelerate and reduce the cost for reproducing and applying.
		%
\end{enumerate}

@@

@@

@@

>>>>

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}

@@

% contributions
In brief, our contribusions include:
%
\begin{enumerate}
	%
	\item Hardness manipulation is proposed for the adversarial training
		of triplet-based deep metric learning models, which avoids model
		collapse in the typical min-max adversarial training setting.
		\oo{We discover that blah}.
		Our proposed method achieves higher adversarial robustness compared
		to the state-of-the-art.
		%
	\item Combine and even better.
		%
	\item Accelerate and reduce the cost for reproducing and applying.
		%
\end{enumerate}

To be investigated: (1) hardness manipulation and analysis of sample
hardness to adversarial trainining of a deep metric learning model.
(2) faster adversarial training by adopting the idea of free adversarial
training. (3) other metric learning loss functions. / free adversarial
training?

@@

\subsection{Evaluation Protocol}

\textbf{Dataset.}

@@

1. adversarial training speed.

@@

\input{appendix.tex}
